---
title: "Perfect Garden"
author: "Tam Nguyen"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)         # for graphing and data cleaning
library(lubridate)         # for working with dates
# For the garden data, you need to first install the remotes library, if you haven't already
# Then, install the gardenR library, if you haven't already. Do this by uncommenting the code below (delete the hashtag) and running it. Then, you should delete this line of code or add the hashtag back so you don't reinstall each time.
# remotes::install_github("llendway/gardenR")
# Once the library is installed, you don't need to install it again, but each time you need to load the library using the code below. You will know if you haven't installed the library if the code below produces an error.
library(gardenR)
# theme_set(theme_minimal())  # set a theme if desired
library(ggthemes)
remotes::install_github("AllanCameron/geomtextpath")
library(geomtextpath)
```

```{r data}
# load the garden data 
data(garden_harvest)
```

Explain the question you hope to answer and create the graph below in the Graph Week 1 section. For the first week, you may not have the skills quite yet to create exactly what you want to create - that's ok! Get as close as you can, and the instructors will give you feedback to help you out. You can summarize the data in any way you'd like. Add R code chunks and comment code as needed. As the weeks go by, you will continue to build on this file by putting new code in the next Graph sections. You will keep all the old code, add your instructor's feedback by copying and pasting it from moodle (found in the Grade section of moodle), and make improvements from my suggestions and from other ideas you have. Having the old code and graphs and the instructor feedback will help you (and the instructors) easily see the progress throughout the course.

FYI, Prof. Lisa just added 2021 data to the `gardenR` package. If you want to use that data (either with the 2020 data or by itself), you will need to reinstall the package. Just a warning that variable names were maintained but names of vegetables and varieties changed in a few cases over the two years (oops). After you load the dataset, you can search for gardenR in the Help tab to find out more about the new datasets.

## Graph Week 1

Question I hope to answer: 

*Which variety of lettuce gave the most yield in pounds over the time period?* 

```{r}
  garden_harvest %>% 
  filter(vegetable %in% c("lettuce")) %>% 
  mutate(weight_lbs = weight*0.00220462)%>% 
  group_by(variety,date) %>% 
  summarize(sum_weight = sum(weight_lbs)) %>% 
  mutate(cum_sum_weight = cumsum(sum_weight)) %>% 
  ggplot(aes(x=date, y = cum_sum_weight, color = variety))+
  geom_line()

  


```

Instructor's feedback: 	Good start. Add a title that captures what's on the x and y axes and omit those axis labels. Use a str_XXX() function to capitalize the first initial of each variety. Remove the vertical grid lines using theme().


## Graph Week 2

Question I hope to answer: *What is the total amount of each variety of tomatoes collected on each day of the week?* 

```{r, fig.alt = "Bar graph showing total harvest of each tomato variety in pounds by day of week. For Better Boy, Jet Star and Old German, there was one certain day each variety was not collected at all" }
garden_harvest %>% 
  filter(vegetable %in% c("tomatoes")) %>% 
  mutate(weight_lbs = weight*0.00220462,, day_of_week = wday(date, label = TRUE, abbr = TRUE))%>% 
  group_by(variety,day_of_week) %>% 
  summarize(total_weight_lbs = sum(weight_lbs)) %>% 
  mutate(variety2 = str_to_title(variety)) %>% 
  ggplot(aes(x = total_weight_lbs, y= fct_rev(fct_relevel(day_of_week, "Mon","Tue","Wed","Thu","Fri","Sat","Sun" ))))+
  geom_col()+
  facet_wrap(vars(variety2))+ 
  labs(y="",
       x="",
       title = "Total Harvest of Each Tomato Variety in Pounds According To Day of Week")+
  theme(panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank())
  
```

Instructor's feedback: 	
Ok - you've created a completely different graph. That's ok, but from now on, you'll work on the same graph until the end. Order the varieties from most to least total harvest weight. Use scale_x_continuous(expand = c(0,0)) to move the y-axis labels right next to the bars.

## Graph Week 3

*Sorry I created two completely different plots. From now on I'll be using the line graph I created for week 1*

Question I hope to answer: *Which variety of lettuce gave the most yield in pounds over the time period?* 

```{r, fig.alt = "Line graph showing cumulative harvest of each lettuce varieties. Lisa appeared to collect Lettuce Mixture variety the most", fig.width = 9, fig.height = 4}
  garden_harvest %>% 
  filter(vegetable %in% c("lettuce")) %>% 
  mutate(weight_lbs = weight*0.00220462)%>% 
  group_by(variety,date) %>% 
  summarize(sum_weight = sum(weight_lbs)) %>% 
  mutate(cum_sum_weight = cumsum(sum_weight)) %>% 
  ggplot(aes(x=date, y = cum_sum_weight, color = str_to_title(variety)))+
  geom_line()+
  labs(title = "Cumulative Weight in pounds for Lettuce Varieties",
       x = "",
       y = "",
       color = "Variety",
       caption = "Line graph by Tam Nguyen")+
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())+
  theme_economist() 
```

Instructor's feedback: 	
This looks great! Make sure to stick with this one for the last one you submit. Omit the legend and instead directly label each line - see the shared google doc on the moodle page for some resources.

## Graph Week 4

Question I hope to answer: *Which variety of lettuce gave the most yield in pounds over the time period?* 


```{r, fig.alt = "Line graph showing cumulative harvest of each lettuce varieties. Lisa appeared to collect Lettuce Mixture variety the most", fig.width = 9, fig.height = 4}
  garden_harvest %>% 
  filter(vegetable %in% c("lettuce")) %>% 
  mutate(weight_lbs = weight*0.00220462)%>% 
  group_by(variety,date) %>% 
  summarize(sum_weight = sum(weight_lbs)) %>% 
  mutate(cum_sum_weight = cumsum(sum_weight), variety2 = str_to_title(variety)) %>% 
  ggplot(aes(x=date, y = cum_sum_weight, color = variety2))+
  geom_line()+
  geom_textline(aes(label = variety2), size = 3, vjust = -0.5)+
  labs(title = "Cumulative Weight in pounds for Lettuce Varieties",
       subtitle = "The graph below shows different lettuce varieties Lisa planted and harvested in her garden",
       x = "",
       y = "",
       caption = "Source: Data by Lisa Lendway, line graph by Tam Nguyen")+
  theme_economist() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none")
```

Instructor's feedback: Looks great! Submit as is!

## Graph Week 5

Question I hope to answer: *Which variety of lettuce gave the most yield in pounds over the time period?* 


```{r, fig.alt = "Line graph showing cumulative harvest of each lettuce variety. Lisa appeared to collect Lettuce Mixture variety the most", fig.width = 9, fig.height = 4}
  garden_harvest %>% 
  filter(vegetable %in% c("lettuce")) %>% 
  mutate(weight_lbs = weight*0.00220462)%>% 
  group_by(variety,date) %>% 
  summarize(sum_weight = sum(weight_lbs)) %>% 
  mutate(cum_sum_weight = cumsum(sum_weight), variety2 = str_to_title(variety)) %>% 
  ggplot(aes(x=date, y = cum_sum_weight, color = variety2))+
  geom_line()+
  geom_textline(aes(label = variety2), size = 3, vjust = -0.5)+
  labs(title = "Cumulative Weight in pounds for Lettuce Varieties",
       subtitle = "The graph below shows different lettuce varieties Lisa planted and harvested in her garden",
       x = "",
       y = "",
       caption = "Source: Data by Lisa Lendway, line graph by Tam Nguyen")+
  theme_economist() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none")
```

Instructor's feedback: (copy the feedback from moodle here)

